Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-05-17 structured.tex
2015.05.16 (Alex & Vassilis) Extensive re-wording throughout the paper. Abstract on its one file. Better figure scaling and alignment. Re-ordering of algorithms in the histogram figures to match paper order of appearence and the table ordering.

This section offers description and analysis of algorithms proposed
to address the topology mismatch problem in structured \p\ networks. 
The categorization of the approaches is based on how different
levels of proximity information is gathered as well as  
the way peer routing tables are maintained and used in an effort make hops in
overlays as efficient as possible. 
%%AD what does it really mean this below???
%%VM it means that this split into i) geographic layout, ii) proximity routing
%%   and iii) proximity neighbour selection types of algorithms are terms
%%   coined in those papers
The categorization is based on previous work found in the
literature~\cite{CDHR2002,CDCR2002,RSS2002}.

@@

%%
Although this approach does reduce the routing latency to far nodes, it
can become expensive as it is 
possible to end up with a very large number of regions
each of which has to maintain a map. 
The fact that a peer may appear in multiple
such maps points into additional traffic for probing and notifications
and so renders the approach not scalable \cite{RGJZ2004}. 
Moreover, to refine measurements
additional inner-bin measurements are needed~\cite{WZS2004}.
Also, improvements within a region can be minimal as there exists
limited knowledge about neighboring zones.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% COMM Removed most of the paragraph below which 
%%		contains info that we cannot back
%%
%% Rescanned papers and wrote the paragraph below.
%% DO NOT PERMANENTLY DELETE!
%%
% Unfortunately, maintained of several host states at different layers,
% renders any content migration a costly process. Additionally, the method does
% not make any continuing effort to remap
% the overlay structure after nodes successfully join resulting into poor
% adaptation to changing conditions. Although this approach greatly reduces the
% routing latency to far nodes, it is unable to dynamically identify nodes that
% are close to routers and gateways in order to construct the secondary overlay.
% Nevertheless, static recognition of such nodes is currently done based on BGP
% reports and pre-chosen landmarks, sacrificing the self-organizing attribute of
% traditional DHTs.
%
%
% TODO: SOME DISCUSSION
%
% Xu \textit{et al.} \cite{XTZ2003} state that there are three ways
% generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multi-cast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighborhood to obtain reasonable results.
%
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in
%which
%the search might be caught into.
%
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well
%suited
%for differentiating nodes within close distance to each other.
%
%\end{itemize}
%
%
%
% TODO: IN PAPER INTRODUCTION A DISCUSSION ABOUT
%TOPOLOGY-AWARE CAN
%
%Techniques to exploit topology information in overlay
%routing include geographic layout, proximity routing and
%proximity neighbor selection [3]. With geographic layout
%such as topology-aware CAN [12], the overlay structure is
%constrained by underlying network topology. This tech-
%nique, unfortunately, can create uneven distribution of
%nodes in the overlay, increasing the chances of overloading
%nodes and rendering the maintenance cost formidable. Our
%study shows that, for a typical 10,000-node topology-aware
%CAN, 5% nodes occupy 85-98% of the entire Cartesian
%space, and some nodes have to maintain 450-1500 neigh-
%bors. In Proximity routing, physical topology is not consid-
%ered when constructing the overlay.
%
In terms of our $3$ criteria, the approach fares as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximately 50-75%.
medium &
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
high &
% Statically implemented sacrificing the decentralized nature of DHTs and
% thus poorly scaling. Also we can end up with a very large number of regions.
% Because of the fact that a peer may appear in multiple
% such maps we can conclude that additional traffic for probing and notifications
% renders the approach does not scalable.
low
\end{tabular}
}
\end{center}

@@

During bootstrap, an incoming peer, say J, starts with a set of
candidates to establish links with and iteratively
probes for minimizing distances, based on a given metric (i.e., network delay)
and concluding when no further refinement can be achieved. To tackle the local
minima problem that such a gradient descent method suffers from, Mithos probes
all neighbours within a two-hop radius, from the currrent node that minimize
the distance, before concluding the process.

Next, the incomming peer is assigned a synthetic \emph{ID} that
represents the state of minimum distance from its close--by neighbourhood as
this was identified during the iterative neighbor selection phase described
above. The benefit of these synthetic coordinates is that distance computations
among nodes can be done in the \emph{ID} space without requiring physical
measurements. The actual link establishment with the peers, that will be J's
neighbours, is happening next. With peer J dividing the plane into four regions,
the \emph{quadrant-based} mechanism Mithos employs, suggests that the node
establishes a link to the closest neighbor in each quadrant of the plane. The
previous steps
do not provide any knowledge as to which nodes these would be, thus J has to
identify them. It does so, by starting from a known node in the neighbourhood
and scanning towards all quadrant borders ~\cite{KK2000,R2002}.

One major limitation of \emph{Mithos} is that the protocol cannot effectively
handle dynamic arrivals and departures from the network. 
\cite{CCRK2004}~argues about extensive probing to determine 
distances and less accurate proximity results compared to other
virtual coordinate systems. The latter has been also attributed
by~\cite{WSS2005} to the iterative neighbor selection process which that is 
reportedly prone to premature termination at local minima.
%%
\cite{cox_vivaldi_2004} argues that elements of the protocol's
synthetic ID generation require a centralized implementation 
affecting \emph{Mithos}' scalability.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In regard to the $3$ criteria, \emph{Mithos} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It has very good results in reducing communication latency among peers but its
% efficiency is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used throughout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incremental probing is applied in quadrants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{LAPTOP}
%
%%AD what is the nature of the "structure" overlay here???
%% VM the structure is that it is organized as a tree hierarchy.
\emph{LAPTOP} \cite{WLH2007} organizes the overlay 
into a tree-based hierarchy so that 
hops required during message routing be reduced and 
maintenance overhead be minimized.
A caching scheme is also used so as
to further lower routing table update costs. 
It is theoretically shown that 
\emph{LAPTOP} routing path length is bounded by $O(log_d(N))$ and node
joining and leaving in the overlay network is bounded by
$O(d*log_d(N))$ hops in a balanced overlay tree with $N$ representing the
number of nodes and $d$ the maximum degree of each node. 
\emph{LAPTOP} adopts the geographical layout approach  
and constructs its layout in a self-organizing and 
efficient fashion. 
The physical distances are estimated
with round trip times to a few existing nodes in the overlay network.
%%
Each node is assigned a dot-formatted address (e.g., 1.3.4). 
Each octet ranges from
$1$ to $d$.
The assignment process is done by appending a unique octet 
to the address of the parent of each node, while
the root node is assigned address $1$.

@@

During tree traversals, special entries in the routing tables,

@@

longest-prefix match than that of its direct ancestor yielding
a larger, quicker and more cost--effective step through the overlay towards

@@

In order to optimize the underlying network use,
\cite{KLKP2008} introduces proximity
controls over the \emph{vanilla Kademlia} 
protocol's random \emph{ID} assignment.
% The work in this paper
% can also be considered as a more generic study of incorporating proximity into
% iterative lookup algorithms.
In its quest to improve routing performance, the overlay uses 
a cost ``yardstick'' (i.e., metric) provided by the underlying network.
% The overlay tier improves its routing performance using a cost--metric that is
% provided by the underlying tier. 
Such cost information can be acquired by
\begin{inparaenum}[\itshape i\upshape)]
  \item measuring previous lookups,
  \item exchanging or jointly-computing measurements with 
	others, or 
  \item using a local database to look--up information.
\end{inparaenum}

\cite{KLKP2008} exploits $2$ routing techniques: 
\emph{proximity routing selection (PRS)} and 
\emph{proximity neighbor selection (PNS)}.
%%
In \emph{PRS}, the goal is to choose the best next hop while routing a message.
\emph{Plain old Kademlia} (\emph{POK}) always selects the closest--node 
with respect to the \emph{XOR} metric.
With \emph{PRS} in place however, \emph{Kademlia} may also choose 
the node that exhibits the smallest routing cost; in this way, 
it balances a trade-off between the logical overlay and 
actual underlying distances.
%%AD rephrased as above.. the "underlay" I am not sure what it is...
%  but with proximity routing, Kademlia should also choose the node
% that exhibits the smallest underlay metric cost, balancing a trade-off between
% the overlay and underlay progress distances.
%%
%% VM rephrased to not contain the word "underlay". Clean up comment block if OK.
%%
In \emph{PNS}, on the other hand, the goal is to keep peers 
with the least routing cost in the routing table. 
%%AD WHAT is this "least contact cost"?? Sounds funny! CHECK
%% VM rephrased to not contain the word "contact". Clean up comment block if OK.

@@

\emph{Kademlia} proximity injection improves 
locality of connections among peers.
To enhance traffic locality, the use of 
{\sl MaxMind GeoIP} database~\footnote{\url{http://www.maxmind.com}} 
is suggested to form clusters of nearby peers.
To this end, Vivaldi coordinates~\cite{cox_vivaldi_2004} could be 
also used as an alternative for morphing locality. 
\cite{KLKP2008} however suggests that the clustering approach 
when combined with \emph{PRS}/\emph{PNS} helps contain 
$40\%$ of messages within an \emph{ISP} and allows only a $6\%$ 
to go through the backbone.
The behavior of the proposal with respect to the stated criteria is deemed as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Uses static information to cluster nodes which is not the most efficient
% approach in dynamic systems
% PNS reduces lookup latencies by 66\% compared to POK
medium &
% 
medium &
% MaxMind is commercial and cannot be used by FOSS P2P systems. Trying to
% expose information from P2P client can result in security issues.
medium
\end{tabular}
}
\end{center}

@@

\emph{CHOP6} \cite{MT2007} is another Chord-variant DHT; it exploits
the {\sl IPv6} address format, and if available \emph{RTT} information, to 
enable proximity estimation among peers during message routing.

Similar to \emph{Chord}~\cite{stoica_chord_2001}, 
\emph{CHOP6} uses a finger table but each entry now holds hold k>1 candidate
nodes. The next hop for a message is selected to be the one closest to the
destination among those k candidate nodes. This proximity is determined either
by exploiting RTT measurements or, if there is no such yet (i.e. a new peer), by
estimating distance on overlay's ID space. When joining the network, each node
receives a $64$-bit \emph{ID}. It comprises of a random part and a IPv6 prefix
part. The random part is obtained by hashing the node's IP address and port
number and is used to preserve the uniformity of
node assignment. The IPv6 prefix is based on IPv6's global routing prefix.
Because IANA  assigns address blocks to regions (RIRs) which are further
distributed on a national level (NIRs), examining the upper $32$-bits
of an IPv6 address someone can estimate the country or the region to which the
node is connected. Thus, CHOP6's IPv6 prefix ID is used for proximity estimation
if no RTT information is available during routing.

%
%\paragraph{}
% There are three cases in which a node chooses the next hop according to
% information it possesses.
%\begin{itemize}
% \item When no information about RTT is available candidate next hops, the
%  sender just selects a node in the finger table entry which shares the longest
% prefix with the destination.
% \item There is another possibility that after some communication with other
%  nodes, the source node should know of the RTTs to some of the nodes in finger
% table entry. In this case, the source node chooses the one with the smallest
% RTT with probability $p$. If there is a node with no measured RTT then the
% sender can select such a node with probability $1 - p$
% \item In this last case the source node has already communicated with all
%  candidate node in the finger table entry. Thus, the node selects the node
% whose RTT is the smallest with probability $p$, the one with the second
% smallest with probability $q$ and so on, where $0 \leq \ldots < r < q < p < 1$
% and $p+q+r+\ldots \leq 1$
%\end{itemize}
%
With respect to the $3$ qualitative criteria, \emph{CHOP6} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Simple approach that exploits proximity but it is coarse grained and thus not
% efficient.
low &
% Its static nature imposes low overhead to the network
low &
% IPv6 is still not widely applied and supported.
medium
\end{tabular}
}
\end{center}

@@

%%AD a better connection with the mismatch problem has to be made... 
%%		.. in the form of 1-2 lines (or short statements). 
%%
%% VM Added some extra lines and restructured the text
\emph{T2MC}'s~\cite{SLCGZ2008} objective is to diminish the redundant multiple
messages that may unnecessarily cross \emph{AS}-boundaries as these are the
links that cost more to ISPs thus minimizing the effects of the topology
mismatch problem. To achieve that, each node exploits the stable structure of
the Internet routers to help solve a clustering problem. Uses traceroute
logs to detect inter-\emph{AS} boundaries and clusters other peers to near-by and
far-away peers by applying a customized $k$-mean classification
algorithm with $k = 2$ to perform the classification.
Specifically when joining the network, the peer randomly picks an IP and uses
traceroute. Skipping the details of the algorithm, it picks the routers with
minimum and maximum latencies in the above traceroute path as initial centroids
for the ``near'' and ``remote'' sets respectively and after some iterations it
ends up with two sets having the minimum intra-set latency variance. The
router with the minimum hops in the ``remote'' set is set up as the hop
threshold and anything above that is classified as the ``remote'' router cluster
for that peer. Similarly, the router with the maximum hops in the ``near'' set
is important because it denotes an edge gateway. Peers that share the same
edge gateway or other members of the ``near'' router cluster are considered
close-by.

>>>>

This section offers description and analysis of algorithms proposed
to address the topology mismatch problem in structured \p\ networks. 
The categorization of the approaches is based on how different
levels of proximity information is gathered as well as  
the way peer routing tables are maintained and used in an effort to make 
overlays as efficient as possible in terms of hops traversed.
%%AD what does it really mean this below???
%%VM it means that this split into i) geographic layout, ii) proximity routing
%%   and iii) proximity neighbour selection types of algorithms are terms
%%   coined in those papers
Our categirization is based on previous work 
found in~\cite{CDHR2002,CDCR2002,RSS2002}.

@@

Although this approach does reduce the routing latency to far nodes, it
can become expensive as it is 
possible to end up with a very large number of regions
each of which has to maintain a map. 
The fact that a peer may appear in multiple
such maps points into additional traffic for probing and notifications
and so renders the approach not scalable \cite{RGJZ2004}. 
Moreover, to refine measurements
additional inner-bin measurements are needed~\cite{WZS2004}.
Also, improvements within a region can be minimal as there exists
limited knowledge about neighboring zones.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% COMM Removed most of the paragraph below which 
%%		contains info that we cannot back
%% Rescanned papers and wrote the paragraph below.
%% DO NOT PERMANENTLY DELETE!
% Unfortunately, maintained of several host states at different layers,
% renders any content migration a costly process. Additionally, the method does
% not make any continuing effort to remap
% the overlay structure after nodes successfully join resulting into poor
% adaptation to changing conditions. Although this approach greatly reduces the
% routing latency to far nodes, it is unable to dynamically identify nodes that
% are close to routers and gateways in order to construct the secondary overlay.
% Nevertheless, static recognition of such nodes is currently done based on BGP
% reports and pre-chosen landmarks, sacrificing the self-organizing attribute of
% traditional DHTs.
% Xu \textit{et al.} \cite{XTZ2003} state that there are three ways
% generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multi-cast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighborhood to obtain reasonable results.
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in
%which
%the search might be caught into.
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well
%suited
%for differentiating nodes within close distance to each other.
%\end{itemize}
% TODO: IN PAPER INTRODUCTION A DISCUSSION ABOUT
%TOPOLOGY-AWARE CAN
%Techniques to exploit topology information in overlay
%routing include geographic layout, proximity routing and
%proximity neighbor selection [3]. With geographic layout
%such as topology-aware CAN [12], the overlay structure is
%constrained by underlying network topology. This tech-
%nique, unfortunately, can create uneven distribution of
%nodes in the overlay, increasing the chances of overloading
%nodes and rendering the maintenance cost formidable. Our
%study shows that, for a typical 10,000-node topology-aware
%CAN, 5% nodes occupy 85-98% of the entire Cartesian
%space, and some nodes have to maintain 450-1500 neigh-
%bors. In Proximity routing, physical topology is not consid-
%ered when constructing the overlay.
In terms of our $3$ stated criteria, the approach fares as follows:
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximately 50-75%.
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
% Statically implemented sacrificing the decentralized nature of DHTs and
% thus poorly scaling. Also we can end up with a very large number of regions.
% Because of the fact that a peer may appear in multiple
% such maps we can conclude that additional traffic for probing and notifications
% renders the approach does not scalable.
low

@@

During bootstrap, an incoming peer $J$ obtains from a bootstrap node a set of
candidate peers to establish links with. 
Subsequently, the node works iteratively to identify peers that minimize
a given metric (i.e., network delay).
The process stops when no additional peers complying with the above metric 
can be found. 
% 
% and iteratively
% probes for minimizing distances, based on a given metric (i.e., network delay)
% and concluding when no further refinement can be achieved. 
To tackle the local
minima problem that such a gradient descent method suffers from, Mithos probes
nodes within a $2$-hop radius from the current node that helps minimize
the distance before concluding the process.

$J$ is then assigned a synthetic \emph{ID} that
represents the state of minimum distance from its close-by $2$-$d$ neighbourhood as
this was discovered during the aforementioned phase. % iterative selection phase.
The benefit of adopting synthetic coordinates is that distance computations
among nodes can be done in the \emph{ID} space without requiring physical
measurements. 
Mithos proceeds then to designate $J$'s closest neighbours as 
previous steps do not reveal with certainty which these nodes are.
%%
Using Mithos \emph{quadrant-based} mechanism,
$J$  divides the $2$--$d$ space of neighbours in four regions and 
subsequently, establishes a link 
to the closest neighbor in each quadrant of the plane. 
% With peer $J$ dividing the plane into four regions,
% the \emph{quadrant-based} mechanism Mithos employs, suggests that the node
% establishes a link to the closest neighbor in each quadrant of the plane. 
%%
It does so, by starting from a known node in the neighbourhood
and scanning towards all quadrant borders ~\cite{KK2000,R2002}.

A noted Mithos limitation is that the protocol cannot effectively
handle dynamic arrivals and departures from the network~\cite{RGJZ2004}. 
\cite{CCRK2004}~points out extensive probing for Mithos to determine 
distances and less accurate proximity results compared to other
virtual coordinate systems. The last issue  has been also attributed
by~\cite{WSS2005} to the iterative neighbor selection process that is 
reportedly prone to premature termination at local minima.
%%
\cite{cox_vivaldi_2004} argues that elements of the protocol's
synthetic ID generation require a centralized implementation 
affecting Mithos' scalability.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In regard to the $3$ criteria, \emph{Mithos} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It has very good results in reducing communication latency among peers but its
% efficiency is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used throughout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incremental probing is applied in quadrants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{LAPTOP}
%
%%AD what is the nature of the "structure" overlay here???
%% VM the structure is that it is organized as a tree hierarchy.
\emph{LAPTOP} \cite{WLH2007} organizes the overlay 
into a tree-based hierarchy so that 
hops required during message routing be reduced and 
maintenance overhead be minimized.
A caching scheme is also used so as
to further lower routing table update costs. 
It is theoretically shown that 
\emph{LAPTOP} routing path length is bounded by $O(log_d(N))$ and node
joining and leaving in the overlay network is bounded by
$O(d*log_d(N))$ hops in a balanced overlay tree with $N$ representing the
number of nodes and $d$ the maximum degree of each node (i.e., number of links). 
\emph{LAPTOP} adopts the geographical layout approach  
and constructs its layout in a self-organizing and 
efficient fashion. 
The physical distances are estimated
with round trip times to a few existing nodes in the overlay network.
%%
Each node is assigned a dot-formatted address (e.g., 1.3.4) with
each octet ranging from $1$ to $d$.
The assignment process is done by appending a unique octet 
to the address of the parent of each node, while
the root node is assigned address $1$.

@@

During tree traversals, special entries in the routing tables

@@

longest-prefix match than that of its direct ancestor;
this yields a quicker and more cost--effective step through the overlay towards

@@

In order to optimize the underlying network use,
\cite{KLKP2008} introduces proximity
controls over the \emph{vanilla Kademlia}~\cite{maymounkov_kademlia_2002} 
protocol's random \emph{ID} assignment.
% The work in this paper
% can also be considered as a more generic study of incorporating proximity into
% iterative lookup algorithms.
In its quest to improve routing performance, the overlay uses 
a cost ``yardstick'' (i.e., metric) provided by the underlying network.
% The overlay tier improves its routing performance using a cost--metric that is
% provided by the underlying tier. 
Such cost information can be acquired by:
\begin{inparaenum}[\itshape i\upshape)]
  \item measuring previous lookups,
  \item exchanging or jointly-computing measurements with others, or 
  \item using a local database to look--up information.
\end{inparaenum}

\cite{KLKP2008} exploits two routing techniques: 
\emph{proximity routing selection (PRS)} and 
\emph{proximity neighbor selection (PNS)}.
%%
In \emph{PRS}, the goal is to choose the best next hop while routing a message.
\emph{Kademlia} always selects the closest--node 
with respect to the \emph{XOR} metric~\cite{maymounkov_kademlia_2002}.
With \emph{PRS} in place however, \emph{Kademlia} may also choose 
the node that exhibits the smallest routing cost; in this way, 
it balances a trade-off between the logical overlay and 
actual underlying distances.
%%AD rephrased as above.. the "underlay" I am not sure what it is...
%  but with proximity routing, Kademlia should also choose the node
% that exhibits the smallest underlay metric cost, balancing a trade-off between
% the overlay and underlay progress distances.
%%
%% VM rephrased to not contain the word "underlay". Clean up comment block if OK.
%%
In \emph{PNS}, on the other hand, the goal is to keep peers 
with the least routing cost in the routing table. 
%%AD WHAT is this "least contact cost"?? Sounds funny! CHECK
%% VM rephrased to not contain the word "contact". Clean up comment block if OK.

@@

\emph{Kademlia} proximity injection improves 
locality of connections among peers.
To enhance traffic locality, the use of 
{\sl MaxMind GeoIP} database\footnote{\url{http://www.maxmind.com}} 
is suggested to form clusters of nearby peers.
To this end, Vivaldi coordinates~\cite{cox_vivaldi_2004} could be 
also used as an alternative for morphing locality. 
\cite{KLKP2008} however suggests that the clustering approach 
when combined with \emph{PRS}/\emph{PNS} helps contain 
$40\%$ of messages within an \emph{ISP} and allows only a $6\%$ 
to go through the backbone.
The behavior of \cite{KLKP2008} with respect to the stated criteria is deemed as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Uses static information to cluster nodes which is not the most efficient
% approach in dynamic systems
% PNS reduces lookup latencies by 66\% compared to POK
medium &
% 
medium &
% MaxMind is commercial and cannot be used by FOSS P2P systems. Trying to
% expose information from P2P client can result in security issues.
medium
\end{tabular}
}
\end{center}

@@

\emph{CHOP6} \cite{MT2007} is a Chord-variant DHT that exploits
{\sl IPv6} address format as well as available \emph{RTT} information to 
enable proximity estimation among peers during message routing.
%%
Similar to \emph{Chord}~\cite{stoica_chord_2001}, 
\emph{CHOP6} uses a finger table with each entry now holding $k$$>$$1$ candidate
nodes. 
The next hop for a message is selected to be the one closest to the
destination among those $k$ candidate peers. 
This proximity is determined either
by exploiting RTT measurements or, if there is no such information yet 
(i.e., a new peer appears), by
estimating distance on the overlay's ID space.

When joining the network, each node
receives a $64$-bit \emph{ID}. 
It comprises of a random part and the IPv6 prefix which 
is obtained by hashing the node's IP address and port
number; this combination is deployed in an effort  
to preserve the uniformity of node assignment. 
The prefix in question is based on IPv6's global routing prefix.
As IANA\footnote{\url{http://www.iana.org/}}  
assigns address blocks to regions (RIRs) which are further
distributed at national level (NIRs), the first $32$-bits of the address
can estimate the region or the country the node is connected in. 
Thus, CHOP6's IPv6 prefix ID is used for proximity estimation
if no RTT information is available during routing. 
%%
%
%\paragraph{}
% There are three cases in which a node chooses the next hop according to
% information it possesses.
%\begin{itemize}
% \item When no information about RTT is available candidate next hops, the
%  sender just selects a node in the finger table entry which shares the longest
% prefix with the destination.
% \item There is another possibility that after some communication with other
%  nodes, the source node should know of the RTTs to some of the nodes in finger
% table entry. In this case, the source node chooses the one with the smallest
% RTT with probability $p$. If there is a node with no measured RTT then the
% sender can select such a node with probability $1 - p$
% \item In this last case the source node has already communicated with all
%  candidate node in the finger table entry. Thus, the node selects the node
% whose RTT is the smallest with probability $p$, the one with the second
% smallest with probability $q$ and so on, where $0 \leq \ldots < r < q < p < 1$
% and $p+q+r+\ldots \leq 1$
%\end{itemize}
%
With respect to the $3$ qualitative criteria, \emph{CHOP6} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Simple approach that exploits proximity but it is coarse grained and thus not
% efficient.
low &
% Its static nature imposes low overhead to the network
low &
% IPv6 is still not widely applied and supported.
medium
\end{tabular}
}
\end{center}

@@

%%AD a better connection with the mismatch problem has to be made... 
%%		.. in the form of 1-2 lines (or short statements). 
%%
%% VM Added some extra lines and restructured the text
\emph{T2MC}'s~\cite{SLCGZ2008} objective is to diminish the redundant multiple
messages that may unnecessarily cross autonomous system (\emph{AS}) boundaries.
The latter represent links that are the costliest to ISPs and hence, 
mininizing topology mismatches  greatly affects pertinent operational expenditure.
%%
To achieve that, each node exploits the stable structure of
the Internet routers to help solve a clustering problem. 
The algorithm uses {\sl traceroute}-logs to detect inter-\emph{AS} boundaries 
and clusters peers to either nearby or 
far-away groups by applying a customized $k$-mean classification ($k=2$).
%%
When joining the network, the peer randomly picks an IP and uses
traceroute and selects the routers with
minimum and maximum latencies in the above {\sl traceroute} path 
as initial centroids for the ``nearby'' and ``far-away'' sets respectively.
Following an iterative procedure, the node comes up with the two sets 
demostrating minimum intra-set latency variance.
At this stage, routers in the ``far-away'' set are not considered critical.
%%
%%AD skipping the details???? JUST CHECK
% Skipping the details of the algorithm, it picks the routers with
% minimum and maximum latencies in the above traceroute path as initial centroids
% for the ``near'' and ``remote'' sets respectively and after some iterations it
% ends up with two sets having the minimum intra-set latency variance. 
%%
% The router from the ``far-away'' set that presents the closest distance 
% from the peer in terms of hops, is designated as beacon.
% Any node portaying dinstance longer that the above is classified 
% as 
% 
% to the peer, in terms of hops, is designated as a beacon.
% Any node whose distance is measured to be longer that the distance 
% between 
% 
% The router with the minimum hops in the ``remote'' set is set up as the hop
% threshold and anything above that is classified as the ``remote'' router cluster
% for that peer. 
% Similarly, 
In contrast, the router from the ``near'' set
having the maximum number of hops 
from the just-joining peer is key as it denotes an edge--gateway. 
Peers that share the same edge--gateway or other members in the ``nearby'' 
router cluster are considered intra-\emph{AS} neighbors.
%%AD the final phrase for this is missing! So what??? What is achieved? 1 sentence.

Even though {\sl traceroute}
provides detailed information about the network structure, 
its extensive use may create overhead on the overall network structure. 
In this respect, administrators frequently
disable {\sl traceroute} support on their routers this 
undoubtly affects \emph{T2MC}'s operation.
%%
Although overall experimental results have been encouraging, 
\emph{T2MC} is considered rather coarse-grained as it only
classifies neighbours into two groups \cite{QLZG2009}.
%
%T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
%systems and cluster close by peers, thus reducing redundant traffic that crosses
%autonomous system boundaries. T2MC uses a customized k-mean classification
%algorithm with $k=2$ to perform the classification, and exploits the stable
%structure of the Internet routers to guide clustering. The peer chooses the
%minimum and maximum Latency results from the trace-route to initialize the
%centroids of two sets. Then the peer calculates, for all hops along its
%trace-routed path, the peer calculates the absolute distance to these centroids
%of both sets and assigns the routers to that centroid with which it has the
%smaller absolute distance. After that, the mean and variance values are
%calculated and if the variance is larger than a predefined threshold then the
%algorithm sets the two latency mean values as new centroids for the two sets and
%loops again. Ultimately peer will end up with two sets having the minimum
%intra-set variance. The peer, then, chooses the router from the second set with
%the minimum hops attribute and sets it as a threshold. The selected router and
%all others whose hops attribute is larger than the threshold are classified as
%\emph{remote} router cluster. The remaining are classified as \emph{near}. From
%the near class, the peer chooses the one with maximum hops attribute as its edge
%router, and registers it along with all near clusters into the DHT of the
%\p\ overlay. As new peers join the network, those that share the same edge
%router or any of the members of the near router clusters, would form a close
%peer cluster. As Edge routers can provide more valuable information than other
%members of the near set, T2MC was designed to prioritize interaction of peers
%and edge gateways.
%
%
% TODO: SOME DISCUSSION
%
%The use of Trace-route as a tool for implementing the distance measuring
%infrastructure raise concerns about its efficiency and scalability. Being,
%primarily, a network diagnostic utility,
% Even though trace-route provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%
\emph{T2MC} fares as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% trace-route is a very heavy tool and thus incurs excessive burden to the
% network resources.
high &
% Trace-route is categorized as too heavy-weighted and intrusive for use in a
% larger scale system \cite{RKHS2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{PChord}
\emph{PChord} \cite{HLYW2005} is based on the \emph{Chord DHT} and adds
proximity into its routing mechanism. 
To achieve that, the standard finger table
is augmented with a \emph{proximity list} that contains
nodes in the network found close-by in terms of RTT.
%in this way, the next hop can be decided based on both progress
%towards the key and the physical proximity of the candidate nodes.
%%AD
%% I am not sure about the "best progress" term - what does it really mean???
%% VM changed the above slightly to address the above comment. Generally
%% in DHTs when a node receives a search query for a key that it does not have
%% the data for, it routes the request to that node in its routing table that
%% is closest to the key. That is what I mean with best progress to the keys
%% In topology aware systems and topology aware routing we have the requirement
%% that the next hop should be the closest one which in many cases can be
%% a competing requirement with the best progress to the key requirement I
%% just described. 
In this respect, the next hop during routing can be decided based on both the
direction towards the search key and minimizing the cost of that hop.
